% Аргумент {1} ниже включает переопределенный стиль с выравниванием слева
\begin{thebibliography}{1}

\bibitem{smt-logics-picture} SMT-LIB 2 Logics. URL: \url{https://smt-lib.org/logics.shtml} (дата обр. 13.05.2024).

\bibitem{z3-paper} Leonardo de Moura and Nikolaj Bjørner. <<Z3: an efficient SMT solver>>. In proceedings of \textit{Tools and Algorithms for the Construction and Analysis of Systems} (TACAS '2008), pp. 337--340. Springer, 2008.

\bibitem{cvc5-paper} Haniel Barbosa, Clark W. Barrett, Martin Brain, Gereon Kremer, Hanna Lachnitt, Makai Mann, Abdalrhman Mohamed, Mudathir Mohamed, Aina Niemetz, Andres N{\"{o}}tzli, Alex Ozdemir, Mathias Preiner, Andrew Reynolds, Ying Sheng, Cesare Tinelli and Yoni Zohar; Dana Fisman (ed.) and Grigore Rosu (ed.). <<cvc5: {A} Versatile and Industrial-Strength {SMT} Solver>>. In proceedings of \textit{Tools and Algorithms for the Construction and Analysis of Systems} (TACAS '2022), part~{I}, pp. 415--442. Springer, 2022.

\bibitem{yices2-paper} Bruno Dutertre; Armin Biere (ed.) and Roderick Bloem (ed.). <<Yices 2.2>>. In proceedings of \textit{Computer-Aided Verification} (CAV '2014), pp. 737--744. Springer, 2014.

\bibitem{bitwuzla-paper} Aina Niemetz and Mathias Preiner; Constantin Enea (ed.) and Akash Lal (ed.). <<Bitwuzla>>. In proceedings of \textit{Computer-Aided Verification} (CAV '2023), part~{II}, pp. 3--17. Springer, 2023.

\bibitem{smt-comp-paper} Clark Barrett, Leonardo de Moura and Aaron Stump. <<SMT-COMP: Satisfiability modulo theories competition>>. In proceedings of \textit{Computer-Aided Verification} (CAV '2005), pp. 503--516. Springer, 2005.

\bibitem{smt-comp-website} SMT-COMP. URL: \url{https://smt-comp.github.io/} (дата обр. 15.05.2024).

\bibitem{symbex-intro-paper} James C. King. <<Symbolic execution and program testing>>. In \textit{Communications of the ACM}, July 1976, volume 19, number 7, pp. 385--394. Association for Computing Machinery, 1976.

\bibitem{klee-website} KLEE Symbolic Execution Engine. URL: \url{https://klee-se.org/} (дата обр. 15.05.2024).

\bibitem{klee-paper} Cristian Cadar, Daniel Dunbar and Dawson Engler. <<KLEE: Unassisted and Automatic Generation of High-Coverage Tests for Complex Systems Programs>>. In proceedings of \textit{the 8th USENIX conference on Operating systems design and implementation} (OSDI '2008), pp. 209--224. USENIX Association, 2008.

\bibitem{gnn-intro-paper} Franco Scarselli, Marco Gori, Ah Chung Tsoi, Markus Hagenbuchner and Gabriele Monfardini. <<The Graph Neural Network Model>>. In \textit{IEEE Transactions on Neural Networks}, vol. 20, no. 1, pp. 61--80, Jan. 2009. IEEE, 2009.

\bibitem{gnn-quantum-chemistry-paper} Justin Gilmer, Samuel S. Schoenholz, Patrick F. Riley, Oriol Vinyals and George E. Dahl. <<Neural Message Passing for Quantum Chemistry>>. \textit{ArXiv abs:1704.01212} (2017).

\bibitem{gnn-deep-learning-5g} Michael M. Bronstein, Joan Bruna, Taco Cohen and Petar Veli\v{c}kovi\'{c}. <<Geometric Deep Learning: Grids, Groups, Graphs, Geodesics, and Gauges>>. \textit{ArXiv abs:2104.13478} (2021).

\bibitem{gcn-conv-paper} Thomas N. Kipf and Max Welling. <<Semi-Supervised Classification with Graph Convolutional Networks>>. \textit{ArXiv abs:1609.02907} (2017).

\bibitem{gnn-global-overview} Jie Zhou, Ganqu Cui, Shengding Hu, Zhengyan Zhang, Cheng Yang, Zhiyuan Liu, Lifeng Wang, Changcheng Li and Maosong Sun. <<Graph Neural Networks: A Review of Methods and Applications>>. \textit{ArXiv abs:1812.08434} (2021).

\bibitem{fastsmt-paper} Mislav Balunovic, Pavol Bielik and Martin T. Vechev. <<Learning to Solve SMT Formulas>>. \textit{Advances in Neural Information Processing Systems 31} (2018).

\bibitem{gnn-for-scheduling-paper} Jan H\r{u}la, David Moj\v{z}\'{\i}\v{s}ek and Mikol\'{a}\v{s} Janota. <<Graph Neural Networks for Scheduling of SMT Solvers>>. \textit{IEEE 33rd International Conference on Tools with Artificial Intelligence} (ICTAI '2021), pp. 447--451. IEEE, 2021.

\bibitem{neurosat-paper} Daniel Selsam, Matthew Lamm, Benedikt B\"{u}nz, Percy Liang, Leonardo Mendonça de Moura and David L. Dill. <<Learning a SAT Solver from Single-Bit Supervision>>. \textit{ArXiv abs:1802.03685} (2018).

\bibitem{smt-comp-2023-benchmarks} SMT-COMP 2023 benchmarks. URL: \url{https://smt-comp.github.io/2023/benchmarks.html} (дата обр. 20.05.2024).

\bibitem{thealgorithms-github} The Algorithms --- Java. URL: \url{https://github.com/TheAlgorithms/Java} (дата обр. 20.05.2024).

\bibitem{owasp-website} OWASP benchmark. URL: \url{https://owasp.org/www-project-benchmark/} (дата обр. 21.05.2024).

\bibitem{cassandra-website} Apache Cassandra. URL: \url{https://cassandra.apache.org/_/index.html} (дата обр. 21.05.2024).

\bibitem{kafka-website} Apache Kafka. URL: \url{https://kafka.apache.org/} (дата обр. 21.05.2024).

\bibitem{spark-website} Apache Spark. URL: \url{https://spark.apache.org/} (дата обр. 21.05.2024).

\bibitem{utbot-github} UnitTestBot. URL: \url{https://github.com/UnitTestBot/UTBotJava} (дата обр. 21.05.2024).

\bibitem{zookeeper-website} Apache Zookeeper. URL: \url{https://zookeeper.apache.org/} (дата обр. 21.05.2024).

\bibitem{elasticsearch-website} Elasticsearch. URL: \url{https://www.elastic.co/elasticsearch} (дата обр. 21.05.2024).

\bibitem{hbase-website} Apache HBase. URL: \url{https://hbase.apache.org/} (дата обр. 21.05.2024).

\bibitem{guava-website} Google Guava. URL: \url{https://github.com/google/guava} (дата обр. 21.05.2024).

\bibitem{hadoop-website} Apache Hadoop. URL: \url{https://hadoop.apache.org/} (дата обр. 21.05.2024).

\bibitem{rvnn-intro-paper} Alessandro Sperduti and Antonina Starita. <<Supervised neural networks for the classification of structures>>. In \textit{IEEE Transactions on Neural Networks}, vol. 8, no. 3, pp. 714--735, May 1997. IEEE, 1997.

\bibitem{rvnn-intro-paper-2} Paolo Frasconi, Marco Gori and Alessandro Sperduti. <<A general framework for adaptive processing of data structures>>. In \textit{IEEE Transactions on Neural Networks}, vol. 9, no. 5, pp. 768--786, Sept. 1998. IEEE, 1998.

\bibitem{attention-is-all-you-need} Ashish Vaswani, Noam Shazeer, Niki Parmar, Jakob Uszkoreit, Llion Jones, Aidan N. Gomez, Lukasz Kaiser and Illia Polosukhin. <<Attention Is All You Need>>. \textit{ArXiv abs:1706.03762} (2017).

% \bibitem{negative-sampling-paper} Tomas Mikolov, Ilya Sutskever, Kai Chen, Greg Corrado and Jeffrey Dean. <<Distributed Representations of Words and Phrases and their Compositionality>>. \textit{ArXiv abs:1310.4546} (2013).

\bibitem{embeddings-for-numerical-features-paper} Yury Gorishniy, Ivan Rubachev and Artem Babenko. <<On Embeddings for Numerical Features in Tabular Deep Learning>>. \textit{Neural Information Processing Systems} (NeurIPS '2022).

\bibitem{ffm-paper-1} Matthew Tancik, Pratul P. Srinivasan, Ben Mildenhall, Sara Fridovich-Keil, Nithin Raghavan, Utkarsh Singhal, Ravi Ramamoorthi, Jonathan T. Barron and Ren Ng. <<Fourier Features Let Networks Learn High Frequency Functions in Low Dimensional Domains>>. \textit{ArXiv abs:2006.10739} (2020).

\bibitem{ffm-paper-2} Yang Li, Si Si, Gang Li, Cho-Jui Hsieh and Samy Bengio. <<Learnable Fourier Features for Multi-Dimensional Spatial Positional Encoding>>. \textit{ArXiv abs:2106.02795} (2021).

\bibitem{sage-conv-paper} William L. Hamilton, Rex Ying and Jure Leskovec. <<Inductive Representation Learning on Large Graphs>>.  \textit{ArXiv abs:1706.02216} (2017).

\bibitem{transformer-conv-paper} Yunsheng Shi, Zhengjie Huang, Shikun Feng, Hui Zhong, Wenjin Wang and Yu Sun. <<Masked Label Prediction: Unified Message Passing Model for Semi-Supervised Classification>>. \textit{ArXiv abs:2009.03509} (2021).

\bibitem{adam-paper} Diederik P. Kingma and Jimmy Ba. <<Adam: A Method for Stochastic Optimization>>. \textit{ArXiv abs:1412.6980} (2014).

\bibitem{adamw-paper} Ilya Loshchilov and Frank Hutter. <<Decoupled Weight Decay Regularization>>. \textit{ArXiv abs:1711.05101} (2017).

\bibitem{dropout-paper} Nitish Srivastava, Geoffrey E. Hinton, Alex Krizhevsky, Ilya Sutskever and Ruslan Salakhutdinov. <<Dropout: a simple way to prevent neural networks from overfitting>>. In \textit{Journal of Machine Learning Research}, vol. 15, pp. 1929--1958, June 2014. JMLR, 2014.

\bibitem{layer-norm-paper} Jimmy Lei Ba, Jamie Ryan Kiros and Geoffrey E. Hinton. <<Layer Normalization>>. \textit{ArXiv abs:1607.06450} (2016).

\bibitem{lambda-rank-paper} Christopher Burges. <<From ranknet to lambdarank to lambdamart: An overview>>. (2010).

\bibitem{triplet-loss-paper-1} Matthew Schultz and Thorsten Joachims. <<Learning a Distance Metric from Relative Comparisons>>. \textit{Neural Information Processing Systems} (NeurIPS '2003).

\bibitem{triplet-loss-paper-2} Gal Chechik, Varun Sharma, Uri Shalit and Samy Bengio. <<Large Scale Online Learning of Image Similarity Through Ranking>>. In \textit{Journal of Machine Learning Research}, vol. 11, pp. 11--14, June 2009. JMLR, 2010.

% \bibitem{usvm-diploma} Поспелов Сергей Андреевич. <<Проектирование и разработка универсальной символьной виртуальной машины>>. \textit{Бакалаврская выпускная квалификационная работа}. СПбГУ, 2023.

% \bibitem{azat} Валеев Азат Рустамович. <<Добавление признаков композиций в функцию потерь модели MusicTransformer для настраиваемой генерации музыки>>. \textit{Бакалаврская выпускная квалификационная работа}. СПбГУ, 2023.

\end{thebibliography}
